Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-20 Paper.Rmd
some minor changes

Review Length (Depth) could be considered as one of the most important independent variable explaining perceived helpfulness. It might be implemented in different ways but for the majority of the studies it is the word count in a given review. For most of the researchers, longer reviews contain more information about the product. As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, other group of researchers found out that there was a threshold on review length, meaning longer reviews might have useless information in them[@schindler2012; @huang2015]. Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018].

@@

## Some other theory

@@

-   mention that channels can change the way we perceive search and experience goods.

@@

Exploratory Data Analysis(EDA) has no set of procedures to be followed. The way EDA is conducted almost always depends on the context of the research. @jebb2017 discusses that EDA encourages scientific replication if done properly. As a researcher, I believe the same notion that transparently sharing the data that I used in the study increases the research's reproducibility value. I also think that readers or fellow researchers might build a better intiution about the discussion and what goes into the model in this study.

@@

"Total Votes" is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 over 5 Helpful votes or 80 over 100 Helpful votes [@mudambi2010; @choi2020].

@@

In order to decrease the uncertainty, search costs must be reduced. In \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. However, since there are other ways to objectively evaluate a movie, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

As it was mentioned in \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses. Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses. @guo2019 found out that people spent more time when evaluating negative reviews. This may suggest a linear interaction between Review Extremity and Review Length. Since people take more time to evaluate negative reviews, this may indicate that the effect of Review Length is stronger when Review Rating is low. And when a review is longer it is evaluated as more helpful for negatively rated reviews than positively rated reviews. In this case, it is hypothesized that:

@@

Hyphothesis 1 proposed a U-Shape for the relationship between Review Extremity and Perceived Helpfulness. For Search Goods this is true because the linear Rating Extremity coefficient (-0.061, p \< 0.01) has a negative sign and the quadratic Rating Extremity coefficient (0.036, p \< 0.001) has a positive sign. The presence of the significant linear interaction effect between Review Extremity and Review Length accentuates the linear Rating Extremity coefficient (-0.043, p \< 0.001). This means that as reviews get longer negative extreme reviews become more useful. For Experience Goods, on the other hand, both linear (0.026, p \< 0.001) and quadratic (0.006, p \< 0.001) Review Extremity terms are positive. A U-Shaped function can't be observed. However, the significant interaction effect between Review Length and Review Extremity (-0.015, p \< 0.001) suggests that for longer reviews the linear term turns to negative. This means that the function takes a U-Shape after a certain review length. It can also be observed that Search Goods have stronger coefficients than Experience Goods meaning the expected U-Shape is more prominent for Search Goods. Therefore, it can be said that for shorter reviews Hypothesis 1 is partially supported and for longer reviews it is fully supported.

>>>>

Review Length (Depth) could be considered as one of the most important independent variable explaining perceived helpfulness. It might be implemented in different ways but for the majority of the studies it is the word count in a given review. For most of the researchers, longer reviews contain more information about the product. As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, other group of researchers found out that there was a threshold on review length, meaning longer reviews might have useless information in them[@schindler2012; @huang2015]. Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018]. Although very rare, a negative relationship between Review Length and Perceived Helpfulness was also reported [@chatterjee2020; @yang2019].

@@

@@

@@

Exploratory Data Analysis(EDA) has no set of procedures to be followed. The way EDA is conducted almost always depends on the context of the research. @jebb2017 discusses that EDA encourages scientific replication if done properly. As a researcher, I believe the same notion that transparently sharing the data that I used in the study increases the research's reproducibility value. I also think that readers or fellow researchers might build a better intuition about the discussion and what goes into the model in this study.

@@

"Total Votes" is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].

@@

In order to decrease the uncertainty, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. However, since there are other ways to objectively evaluate a movie such as quality of its effects or its budget and how well this budget is utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

As it was mentioned in Section \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses. Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses. @guo2019 found out that people spent more time when evaluating negative reviews. This may suggest a linear interaction between Review Extremity and Review Length. Since people take more time to evaluate negative reviews, this may indicate that the effect of Review Length is stronger when Review Rating is low. And when a review is longer it is evaluated as more helpful for negatively rated reviews than positively rated reviews. In this case, it is hypothesized that:

@@

Hypothesis 1 proposed a U-Shape for the relationship between Review Extremity and Perceived Helpfulness. For Search Goods this is true because the linear Rating Extremity coefficient (-0.061, p \< 0.01) has a negative sign and the quadratic Rating Extremity coefficient (0.036, p \< 0.001) has a positive sign. The presence of the significant linear interaction effect between Review Extremity and Review Length accentuates the linear Rating Extremity coefficient (-0.043, p \< 0.001). This means that as reviews get longer negative extreme reviews become more useful. For Experience Goods, on the other hand, both linear (0.026, p \< 0.001) and quadratic (0.006, p \< 0.001) Review Extremity terms are positive. A U-Shaped function can't be observed. However, the significant interaction effect between Review Length and Review Extremity (-0.015, p \< 0.001) suggests that for longer reviews the linear term turns to negative. This means that the function takes a U-Shape after a certain review length. It can also be observed that Search Goods have stronger coefficients than Experience Goods meaning the expected U-Shape is more prominent for Search Goods. Therefore, it can be said that for shorter reviews Hypothesis 1 is partially supported and for longer reviews it is fully supported.
